\documentclass[]{report}   % list options between brackets

% list packages between braces
\usepackage{titlesec}             % http://ctan.org/pkg/titlesec 

% For changing the table of content entries in to hyperlinks
%\usepackage[linktoc=all]{hyperref}
%\hypersetup{colorlinks=true, linkcolor=blue}

% type user-defined commands here
\renewcommand{\thesection}{}% Remove section references...
\renewcommand{\thesubsection}{\arabic{subsection}}%... from subsections

\begin{document}
\raggedright{}  % Don't allow text to be spread to the right margin

\title{PDP-11 Simulator}   % type title between braces
\author{Benjamin Hunstman \\
Michael Walton\\
Kevin Bedrossian}         % type author(s) between braces
\date{February 01, 2014}    % type date between braces
\maketitle

\begin{abstract}
  A PDP-11/20 Instruction Set Architecture (ISA) simulator.  A Macro-11 assembly program can be compiled and loaded into the simulator and run giving the same functionality as the original system.  This was accomplished using C++ as the framework with Qt5 creating the GUI to gain easy access to view memory space and registers and to follow the assembly code while the instructions are processed.
\end{abstract}

\tableofcontents

\chapter{Introduction}
 The PDP-11/20 ISA simulator is modularized into parts similar to the actual computer hardware.  The CPU object controls the overall functionality of the simulator by managing the fetch, decode, and execute processes.  The steps to this process are as follows: fetch instruction, decode instruction, request data from the Memory object in accordance with the decoded instruction, followed by the appropriate execution of operations and condition code updates.  There is a Memory object that manages the loading of program into the memory block and the flow of reading and writing data. 

\chapter{Design Plan}
Simple object-oriented design techniques were used to implement the simulator application, which were leveraged for development of a GUI using the Qt5 framework\@. The GUI development loosely follows a Model-View-ViewModel framework where we use ViewModel class objects to act as the delegate to propagate changes in the application data to and from the UI\@. The simulator itself uses a top level simulator management class that manages a cpu and memory object as well as the ViewModel classes that interact with the UI\@.

An object-oriented approach was chosen to allow for a standard interface between abstracted simulator components to be defined early on in order to avoid breaking from changes in implementation throughout the project.

\chapter{Test Plan}
Several test cases were written in Macro-11 assembly format in order to demonstrate functionality of the simulator. The 12 test cases written probe for correct design in the following areas:

\begin{itemize}
  \item Addressing modes
  \begin{itemize}
  \item General Register
  \item General Register Deferred
  \item Register Autoincrement\textbackslash Decrement
  \item Register Autoincrement\textbackslash Decrement Deferred
  \item Register Index\textbackslash Index Deferred
  \item Stack Pointer
  \item Program Counter
  \end{itemize}
\item Instructions
  \begin{itemize}
  \item Double Operand
  \item Single Operand
  \item Branches
  \end{itemize}
\item JSR
\end{itemize}

Using states predefined in these documented test cases we can follow the execution in the simulator in order to verify that the architecture is being emulated to specifications properly.

%\begin{thebibliography}{9}
  % type bibliography here
%\end{thebibliography}

\end{document}
